### 2019-02-14 macro3_3.tex
Macro

			&\lim_{t \to \infty} b(t)e^{-\int_{0}^t r(\tau)d\tau} \ge 0, c(t) \ge 0, 0 \le l(t) \le 1, b(0) = 0, a(t) \le 1\\

@@

	&\lim_{t \to \infty} b(t)e^{-\int_{0}^t r(\tau)d\tau} \ge 0, c(t) \ge 0, 0 \le l(t) \le 1, b(0) = 0, \frac{x(t)}{p(t)} \le 1\\

@@

@@

>>>>

			&\lim_{t \to \infty} b(t)e^{-\int_{0}^t r(\tau)d\tau} \ge 0, c(t) \ge 0, 0 \le l(t) \le 1, b(0) = 0, 0 \le a(t) \le 1\\

@@

	&\lim_{t \to \infty} b(t)e^{-\int_{0}^t r(\tau)d\tau} \ge 0, c(t) \ge 0, 0 \le l(t) \le 1, b(0) = 0,0 \le \frac{x(t)}{p(t)} \le 1\\

@@

	\item Using capital motion equation, market clearing can be rewritten as follows:
	c(t) + \dot{k}(t) + \delta k(t) + d(t) = F'_k(k(t), l(t))k(t) + F'_l(k(t), l(t))l(t)\\
	c(t) + \dot{k}(t) + \delta k(t) + d(t) = F'_k(k(t), l(t))k(t) + w(t)l(t)\\
	Since at the equilibrium firms have zero profit, market clearing condition implies that 
	c(t) = w(t)l(t)
	that means that
	\dot{k}(t) + \delta k(t) + d(t) &= (r(t) + \delta)k(t)\\
	r(t) &= \frac{\dot{k}(t) + d(t)}{k(t)}
	$k(t) = p(t)$ i.e. price of asset is equal to price of capital, it is a reasonable result. At equilibrium people should be indifferent between purchasing capital and purchasing assets.

@@

	 Since $a(t) = 1$ then $x(t) = p(t) = k(t)$. Thus,
	\dot{b}(t) + \dot{k}(t) = w(t)l(t) + r(t)b(t) + r(t)k(t) - c(t)
	So, we obtained the budget constraint in a model when consumers own capital.
	\item Again, consumers save through firms: market clearing implies that the whole output should be either consumed by consumers or invested in future capital (or payed consumers in a form of dividends). As a result, consumers are able to reduce consumption and thereby increase investments in future capital which increases their future wages and dividends. $r(t)$ is also set such that consumers and firms become indifferent between different forms of saving (investment).
